### 2020-02-26 thesis/paper.tex
structure

\section{Idea of the Tool}

@@

\subsection{Facilitating Clustering Exploration}
One of the main research questions for the tool was: How to assist users in visually exploring clustering results? To achieve this, both visualizing how similar results are to each other and presenting individual results is of importance.

@@

\subsection{Gathering more Information}
Another research question was: How can we gain knowledge from more computed clusterings, instead of just picking one? I found that the goal of most visual frameworks is to find the best clustering solution out of a bunch of computed ones. Using the information of more than one clustering can result in a better solution though, so finding a way of including it was relevant. Here, this was achieved by using consensus functions which are able to combine multiple clustering solutions into one. This can not only be done by combining all computed solutions but also in combination with finding similar groups. These groups can be combined into one result each, capturing the essence of all included results.

@@

\subsection{Easy Usage of complex Methods/Workflows}
The aspect of how easily a user can use those often complex clustering and consensus clustering methods was also relevant. There are currently no simple tools that allow to use clustering methods, compare them and compute consensus clusterings from them, all in one place. Therefore, an important consideration was to make this process as easy as possible, while not loosing out on the power the methods bring with them. The strategy here was to clearly separate the pre-processing, the definition of the clustering algorithms and the exploration and merging of the results. To also enable the use of future or currently missing methods, the extendability of the tool was of importance, this is achieved through interfaces with which such methods can easily be added.

>>>>

\chapter{Idea of the Tool}\label{cha:idea}

@@

\section{Facilitating Clustering Exploration}
One of the main research questions for the tool was: How to assist users in visually exploring clustering results? To achieve this, both visualizing how similar results are to each other and presenting individual results is of importance.

@@

\section{Gathering more Information}
Another research question was: How can we gain knowledge from more computed clusterings, instead of just picking one? I found that the goal of most visual frameworks is to find the best clustering solution out of a bunch of computed ones. Using the information of more than one clustering can result in a better solution though, so finding a way of including it was relevant. Here, this was achieved by using consensus functions which are able to combine multiple clustering solutions into one. This can not only be done by combining all computed solutions but also in combination with finding similar groups. These groups can be combined into one result each, capturing the essence of all included results.

@@

\section{Easy Usage of complex Methods/Workflows}
The aspect of how easily a user can use those often complex clustering and consensus clustering methods was also relevant. There are currently no simple tools that allow to use clustering methods, compare them and compute consensus clusterings from them, all in one place. Therefore, an important consideration was to make this process as easy as possible, while not loosing out on the power the methods bring with them. The strategy here was to clearly separate the pre-processing, the definition of the clustering algorithms and the exploration and merging of the results. To also enable the use of future or currently missing methods, the extendability of the tool was of importance, this is achieved through interfaces with which such methods can easily be added.
